LDA exploration

### 2016-01-28 doc/manuscript.Rmd
Added results for lda, dev discuss, added caps and figs

- as GEE results suggest that % does nothing, but in conc 16:0 etc has assoc...
is it that 16:0 is harmful or is it the pool? is it that as 16:0 inc, there is
harm, irrespective of whether other FA increase or decrease as well?
- need to do LDA or some such to id the pattern of why... (don't show this in
paper, but examine PCA of it too)

@@

- sleep restriction can impact NEFA, but only higher during night and a bit
during early-morning. Should keep this in mind.
- Adjust for TAG in IR models?

@@

tab_basic <- tab('basicChar', 'Basic characteristics of the PROMISE participants at each of the 3 time points.')
fig_dist <- fig('nefaDist', 'Concentrations (nmol/mL) of each non-esterified fatty acid in PROMISE participants at the baseline visit (2004-2006)')
fig_gee <- fig('gee', 'Longitudinal associations of individual non-esterified fatty acids (mol% and nmol/mL) with insulin sensitivity and beta-cell function using generalized estimating equations over the 6 years in the PROMISE cohort.  Adjusted for {{covariates}}. Outcome variables were log-transformed, predictor variables were scaled, and x-axis values were exponentiated to represent percent difference per SD increase in the fatty acid.  P-values presented were adjusted for the false discovery rate.')
```

@@

The Prospective Metabolism and Islet cell Evaluation (PROMISE) cohort is a
longitudinal observational study of participants with one or more risk factors
for type 2 diabetes mellitus, including obesity, hypertension, family history of
diabetes, and/or a history of gestational diabetes or birth of a macrosomic 
infant.  Participants aged 30 years and older were recruited for the baseline
visit from Toronto and London, Ontario, Canada into the PROMISE cohort (n=736) 
between 2004-2006.  Follow-up examinations occur every three years, with
currently three examination visits completed to date (2004-2006, 2007-2009, and
2010-2013).  The current study used data on participants who did not have
diabetes at baseline, who returned for one or more follow-up examinations, and
who had samples available for fatty acid measurements (n=477).  A diagram of the
sample size at each visit is shown in `r supFigRef('flow')`.  At each
examination, participants undergo extensive metabolic characterization, 
anthropometric measurements, and structured questionnaires on lifestyle and
sociodemographics.  Research ethics approval was obtained from Mount Sinai
Hospital and the University of Western Ontario.  Data collection methods were
standardized across the 2 centres and research nurses were centrally trained. 
<!--Over the 6-yrs, {{n return each visit}} returned for the 6-yr clinic visit 
({{pct loss to followup}}% loss to follow-up).  By the 6-yr visit, {{n converted
to IFG}} converted into IFG, {{n converted to IGT}} converted into IGT, and {{n
converted to DM}} into diabetes.-->

@@

At each clinic examination, participants had an 7-12 hour fasting blood sample 
taken and then had a 75g oral glucose tolerance test (OGTT) with a 30 minute and
2 hour blood draw. All blood samples were processed and frozen at -70°C. Alanine
aminotransferase (ALT) was measured using standard laboratory procedures. 
Cholesterol, HDL, and triacylglycerols (TAG) were measured using Roche Modular's
enzymatic colometric tests (Mississauga, ON).  Both specific insulin and glucose
were derived from the OGTT at fasting, 30 minute, and 2 hour time points. 
Specific insulin was measured using the Elecsys 1010 (Roche Diagnostics, Basel, 
Switzerland) immunoassay analyzer and electrochemiluminescence immunoassay. 
This assay shows 0.05% cross-reactivity to intact human pro-insulin and the Des
31,32 circulating split form (Linco Res. Inc), and has a CV of 9.3%.  Glucose
was determined using an enzymatic hexokinase (Roche Modular, Roche Diagnostics)
with a detection range of 0.11 (2 mg/dL) to 41.6 mmol/L.  The inter-assay %CV is
<1.1% and intra-assay %CV is < 1.9%.  All assays were performed at the Banting 
and Best Diabetes Centre Core Lab at the University of Toronto. Impaired fasting
glucose (IFG), impaired glucose tolerance (IGT), and diabetes were categorized
using the 2006 WHO criteria [@WHO2006].

@@

Insulin sensitivity and beta-cell function indices were computed using the OGTT
glucose and insulin.  Insulin sensitivity was assessed using the inverted
homeostasis model assessment of insulin resistance (1/HOMA-IR) [@Matthews1985]
and the Insulin Sensitivity Index (ISI) [@Matsuda1999]. HOMA-IR largely reflects
hepatic insulin resistance, while ISI reflects whole-body insulin sensitivity
[@AbdulGhani2007].  Beta-cell function was assessed using the Insulinogenic
Index [@Wareham1995] over HOMA-IR (IGI/IR) and the Insulin Secretion-Sensitivity
Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR is a measure of the first phase
insulin secretion while ISSI-2 is analogous to the disposition index. Each index
has been validated against gold standard measures [@Matthews1985; @Matsuda1999;
@Retnakaran2009].

@@

Height, weight, and waist circumference (WC) were measured at all clinic
examinations using standard procedures.  WC was measured at the natural waist,
defined as the narrowest part of the torso between the umbilicus and the xiphoid
process.  Height was measured using a stadiometer and weight was measured on a 
medical balance beam scale. BMI was calculated by dividing weight (kg) by height
(m) squared. Sociodemographic information, such as age, sex, and ethnicity, were
determined using standardized questionnaires administered at each examination
visit.

@@

Covariates selection was based on previous literature, suggestions from directed
acyclic graph modeling [@Greenland1999a], and the quasi-likelihood information
criterion (QIC). Various models compared using QIC are shown in **`r supTabRef('tabQIC')`**.  
The final GEE model (M#) we selected had time, sex,
ethnicity, baseline age, waist circumference, {{...}}, and family history of
diabetes as covariates.  GEE parameter estimates were exponentiated.
<!--(exponentiated, minus 1, and multiplied by 100)--> After scaling,
log-transforming, and exponentiating, the GEE parameter estimates are
interpreted as an expected percent difference in the outcome variable for every
SD increase in the predictor variable given the covariates are held constant. 
An time by predictor term was included in each of the GEE models to test for
time interactions.

Sensitivity analysis adjusting for clinically measured TG, as TG at the 6 year
visit was only done on a subset of participants.

While the GEE modeling takes into consideration the longitudinal design of the
data, a limitation is that it can not analyze the inherent multivariate nature
of the composition of the NEFA fraction. As such, after running the GEE models
for the longitudinal analysis, linear discriminant analysis (LDA) {{or QDA}} was
used to identify the patterns of NEFA composition for tertiles of the metabolic
disorders. LDA is not suited for longitudinal data and so only the baseline
visit data was used and only the outcome and predictor variables could be
included in the analysis. Data from the later visit dates were used to confirm
the results of the LDA analysis.

All statistical tests were computed using R `r getRversion()`
[@Rbase], along with the R packages geepack `r packageVersion('geepack')` for
the GEE modeling [@Hoejsgaard2006a] and MASS `r packageVersion('MASS')` for LDA.
The R code for this manuscript is available at {{link}}. Results were
statistically significance at p<0.05, after adjusting for the False Discovery
Rate [@Benjamini1995a] for multiple testing.

@@

```{r geeData, cache=TRUE}

outcomes_is <- c('linvHOMA', 'lISI')
outcomes_bcf <- c('lIGIIR', 'lISSI2')
outcomes <- c(outcomes_is, outcomes_bcf)
ne_pct <- grep('^pct_ne', names(ds), value = TRUE)
ne_conc <- c('ne_Total', grep('^ne\\d\\d', names(ds), value = TRUE))
covariates_is <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT')
covariates_bcf <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 
                    'MET', 'AlcoholPerWk')

@@

```{r ldaData}
# include also the 3-yr and 6-yr data for training/testing.
lda_df <- ds %>%
    filter(VN == 0) %>%
    mutate(BCF = rstatsToolkit::aide.tertile(lISSI2) %>%
               factor(., labels = c('1st tertile: log(ISSI-2)', 
                                    '2nd tertile: log(ISSI-2)', 
                                    '3rd tertile: log(ISSI-2)'), 
                      ordered = TRUE)) %>%
    select(BCF, matches('^ne\\d\\d')) %>%
    mutate_each(funs(as.numeric(scale(.))), -BCF) %>%
    na.omit() %>% 
    arrange(BCF)
lda_results <- lda(BCF ~ ., data = lda_df)
```

```{r resultsInline, dependson='geeData'}
# extract gee beta coefficient for indicating magnitude
pctChg.o <- ds %>%
  select(f.VN, HOMA, ISI, IGIIR, ISSI2) %>%
  gather(Measure, Value, -f.VN) %>%
  na.omit() %>%
  group_by(Measure, f.VN) %>%
  summarise(med = median(Value)) %>%
  spread(f.VN, med) %>%
  mutate(pctChg = ((`6-yrs` - `0-yr`) / `0-yr`) * 100) %>%
  select(pctChg) %>%
  abs() %>%
  round(1) %>%
  {paste0(min(.), '% to ', max(.), '%')}

cumPctPL <- calcCumPctFA(ds, 'pct_pl', 90)
calcCumPctFA <- function(data, variable.pattern, filter.value) {
    data %>%
      filter(VN == 0) %>%
      select(matches(variable.pattern)) %>%
      gather(fat, value) %>%
      group_by(fat) %>%
      summarise(pct = mean(value, na.rm = TRUE)) %>%
      arrange(desc(pct)) %>%
      mutate(cumpct = cumsum(pct) %>% round(1) %>% format(nsmall = 1),
             pct = round(pct, 1) %>% format(nsmall = 1)) %>%
      filter(cumpct <= filter.value)
}
extractBeta <- function(data) {
    data %>%
      mutate(estCI = paste0('(beta: ', trim(format(round(estimate, 1), nsmall = 1)),
                            ' CI: ',
                            trim(format(round(conf.low, 1), nsmall = 1)),
                            ', ',
                            trim(format(round(conf.high, 1), nsmall = 1)),
                            ')'),
             #indep.estCI = paste(indep, estCI),
             #dep = paste(dep %>% gsub('log\\((.*)\\)', '\\1', .), estCI),
             dep = paste(dep %>% gsub('log\\((.*)\\)', '\\1', .))
             ) %>%
      filter(p.value <= 0.05) %>%
      arrange(dep, desc(estimate)) %>%
      select(dep, indep, estCI)
}
```

@@

@@

@@

Brief overall conclusion...

@@

Comment on LDA analysis... ...LDA backs up some of the GEE model results,
showing weak discriminatory ability of the NEFA pattern on identifying beta-cell
function... ...While the overall discriminatory ability of the NEFA pattern was
poor, there were certain NEFA that loaded differently on each level of beta-cell
function....

@@

```{r figDist}
ds %>%
    filter(VN == 0) %>%
    select(SID, matches('^ne\\d')) %>%
    filter(complete.cases(.)) %>% 
    gather(Measure, Value, -SID) %>% 
    mutate(Measure = renaming_fa(Measure) %>% 
               gsub('ne_', '', .) %>%
               factor(., levels = unique(.))) %>% 
    spread(Measure, Value) %>% 
    select(-SID) %>% 
    trance('boxes_dots') %>% 
    visualize(dots = FALSE,
              xlab = 'Concentration (nmol/mL)',
              ylab = 'Non-esterified fatty acid') %>% 
    vision_simple() +
    theme(axis.ticks.y = element_blank())
```

```{r figGEE, dependson='geeData'}
forest_plot(gee_results)
```

```{r figLDA}
visualize(lda_results, 'means', label.rename.fun = renaming_fa) %>% 
    vision_simple() +
    labs(y = 'Non-esterified fatty acids',
         x = 'Standardized mean of the fatty acid (SD of the nmol/mL)')
```

@@

```{r supFigGeeUnadj, dependson='geeData'}
forest_plot(gee_results_unadj)
```

>>>>

- as GEE results suggest that % does nothing, but in conc 16:0 etc has assoc...
is it that 16:0 is harmful or is it the pool? is it that as 16:0 inc, there is
harm, irrespective of whether other FA increase or decrease as well?

@@

- sleep restriction can impact NEFA, but only higher during night and a bit
during early-morning. Should keep this in mind.
- Adjust for TAG in IR models?
- Key is that this is fasting, not postprandial!

@@

tab_basic <- tab('basicChar', 'Basic characteristics of the PROMISE participants at each of the 3 time points.')
fig_dist <- fig('nefaDist', 'Concentrations (nmol/mL) of each non-esterified fatty acid in PROMISE participants at the baseline visit (2004-2006)')
fig_gee <- fig('gee', 'Longitudinal associations of individual non-esterified fatty acids (mol% and nmol/mL) with insulin sensitivity and beta-cell function using generalized estimating equations over the 6 years in the PROMISE cohort.  Adjusted for {{covariates}}. Outcome variables were log-transformed, predictor variables were scaled, and x-axis values were exponentiated to represent percent difference per SD increase in the fatty acid.  P-values presented were adjusted for the false discovery rate.')
fig_lda <- fig('lda', 'Linear discriminant analysis to identify patterns of NEFA composition between tertiles of log(ISSI-2) in 463 PROMISE participants at the baseline visit (2004-2006).')

sfig_consort <- sfig('consort', 'CONSORT diagram....')
sfig_lda <- sfig('lda', 'Linear discriminant factors with explained variance against tertiles of log(ISSI-2) in 463 PROMISE participants at the baseline visit (2004-2006).')
```

@@

The Prospective Metabolism and Islet cell Evaluation (PROMISE) cohort is a 
longitudinal observational study of participants with one or more risk factors 
for type 2 diabetes mellitus, including obesity, hypertension, family history of
diabetes, and/or a history of gestational diabetes or birth of a macrosomic 
infant.  Participants aged 30 years and older were recruited for the baseline 
visit from Toronto and London, Ontario, Canada into the PROMISE cohort (n=736) 
between 2004-2006.  Follow-up examinations occur every three years, with 
currently three examination visits completed to date (2004-2006, 2007-2009, and 
2010-2013).  The current study used data on participants who did not have 
diabetes at baseline, who returned for one or more follow-up examinations, and 
who had samples available for fatty acid measurements (n=477).  A diagram of the
sample size at each visit is shown in `r cite_sf('consort')`.  At each 
examination, participants undergo extensive metabolic characterization, 
anthropometric measurements, and structured questionnaires on lifestyle and 
sociodemographics.  Research ethics approval was obtained from Mount Sinai 
Hospital and the University of Western Ontario.  Data collection methods were 
standardized across the 2 centres and research nurses were centrally trained. 
<!--Over the 6-yrs, {{n return each visit}} returned for the 6-yr clinic visit 
({{pct loss to followup}}% loss to follow-up).  By the 6-yr visit, {{n converted
to IFG}} converted into IFG, {{n converted to IGT}} converted into IGT, and {{n 
converted to DM}} into diabetes.-->

@@

At each examination, participants had an 8-12 hour fasting blood sample 
taken followed by a 75g oral glucose tolerance test (OGTT) with a 30 minute and
2 hour blood draw. All blood samples were processed and frozen at -70°C. {{Alanine
aminotransferase (ALT) was measured using standard laboratory procedures.}} 
Cholesterol, HDL, and triglycerides (TG) were measured using Roche Modular's
enzymatic colometric tests (Mississauga, ON).  Both specific insulin and glucose
were derived from the OGTT at fasting, 30 minute, and 2 hour time points. 
Specific insulin was measured using the Elecsys 1010 (Roche Diagnostics, Basel, 
Switzerland) immunoassay analyzer and electrochemiluminescence immunoassay. 
This assay shows 0.05% cross-reactivity to intact human pro-insulin and the Des
31,32 circulating split form (Linco Res. Inc), and has a CV of 9.3%.  Glucose
was determined using an enzymatic hexokinase (Roche Modular, Roche Diagnostics)
with a detection range of 0.11 (2 mg/dL) to 41.6 mmol/L.  The inter-assay %CV is
<1.1% and intra-assay %CV is < 1.9%.  All assays were performed at the Banting 
and Best Diabetes Centre Core Lab at the University of Toronto. Impaired fasting
glucose (IFG), impaired glucose tolerance (IGT), and diabetes were categorized
using the 2006 WHO criteria [@WHO2006].

@@

Insulin sensitivity and beta-cell function indices were computed using the OGTT 
glucose and insulin.  Insulin sensitivity was assessed using 1/HOMA-IR (1
divided by HOMA-IR) [@Matthews1985] and the Insulin Sensitivity Index (ISI)
[@Matsuda1999]. HOMA-IR largely reflects hepatic insulin resistance, while ISI
reflects whole-body insulin sensitivity [@AbdulGhani2007].  Beta-cell function
was assessed using the Insulinogenic Index [@Wareham1995] over HOMA-IR (IGI/IR)
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2) [@Retnakaran2009]. IGI/IR
is a measure of the first phase insulin secretion while ISSI-2 is analogous to
the disposition index. Each index has been validated against gold standard
measures [@Matthews1985; @Matsuda1999; @Retnakaran2009].

@@

Height, weight, and waist circumference (WC) were measured at all clinic 
examinations using standard procedures.  WC was measured at the natural waist, 
defined as the narrowest part of the torso between the umbilicus and the xiphoid
process. BMI was calculated by dividing weight (kg) by height (m) squared.
Sociodemographic information, such as age, sex, and ethnicity, were determined
using questionnaires administered at each examination.

@@

Covariates selection was based on previous literature, directed acyclic graph
[@Greenland1999a] recommendations, and quasi-likelihood information criterion
(QIC). `r cite_sf('qic')` shows the covariates compared using QIC and 
`r cite_sf('dag')` shows the specified directed acyclic graph. The final GEE model
(M#) we selected had time, sex, ethnicity, baseline age, waist circumference,
{{...}}, and family history of diabetes as covariates. <!--(exponentiated, minus
1, and multiplied by 100)--> After scaling, log-transforming, and exponentiating
the GEE estimates, the GEE results are interpreted as an expected percent
difference in the outcome variable for every SD increase in the predictor
variable given the covariates are held constant. An time by predictor term was
included in each of the GEE models to test for time interactions. Given that TG
is a risk factor for diabetes and that NEFA contribute to TG production, TG may
act as a mediator between NEFA and the outcomes. However, only a subset of the
participants at the 6-yr visit had clinically measured TG. To determine the role
of TG in the association between NEFA and the outcomes, TG was included in the
GEE model as a sensitivity analysis.

While GEE controls for the longitudinal design of the data, a limitation is that
it can not analyze the inherent multivariate nature of the composition of the
NEFA fraction. As such, after running the GEE models for the longitudinal
analysis, linear discriminant analysis (LDA) was used to identify the patterns
of NEFA composition for tertiles of the metabolic disorders. Since LDA can't
handle longitudinal data, only the baseline data was used and only the outcome
and predictor variables could be included in the analysis. Data from the later
visit dates were used to confirm the results of the LDA analysis.

All analyses were performed using R `r getRversion()` [@Rbase], along with the R
packages geepack `r packageVersion('geepack')` for GEE [@Hoejsgaard2006a] and 
MASS `r packageVersion('MASS')` for LDA. The R code for this manuscript is
available at {{link}}. Results were statistically significance at p<0.05, after
adjusting for multiple testing using the False Discovery Rate [@Benjamini1995a].

@@

```{r geeData, cache=TRUE}
outcomes_is <- c('linvHOMA', 'lISI')
outcomes_bcf <- c('lIGIIR', 'lISSI2')
outcomes <- c(outcomes_is, outcomes_bcf)
ne_pct <- grep('^pct_ne', names(ds), value = TRUE)
ne_conc <- c('ne_Total', grep('^ne\\d\\d', names(ds), value = TRUE))
covariates_is <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT')
covariates_bcf <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 
                    'MET', 'AlcoholPerWk')

@@

```{r ldaData}
# include also the 3-yr and 6-yr data for training/testing.
lda_df <- get_lda_data(ds)
lda_results <- lda(BCF ~ ., data = lda_df)
```

```{r inlineGEE, dependson='geeData'}
# extract gee beta coefficient for indicating magnitude
pctChg.o <- ds %>%
  select(f.VN, HOMA, ISI, IGIIR, ISSI2) %>%
  gather(Measure, Value, -f.VN) %>%
  na.omit() %>%
  group_by(Measure, f.VN) %>%
  summarise(med = median(Value)) %>%
  spread(f.VN, med) %>%
  mutate(pctChg = ((`6-yrs` - `0-yr`) / `0-yr`) * 100) %>%
  select(pctChg) %>%
  abs() %>%
  round(1) %>%
  {paste0(min(.), '% to ', max(.), '%')}
```

```{r inlineLDA}
fit.class <- predict(lda_results, newdata = lda_df[, -1])$class %>% 
    factor(., ordered = TRUE)

# Amount of participants who were misclassified
misclass <- table(fit.class, lda_df[[1]]) %>% 
    as.data.frame() %>% 
    filter(fit.class != Var2) %>% 
    summarize(count = sum(Freq)) %>% 
    as.numeric()

# Amount of participants who were correctly classified
good_class <- table(fit.class, lda_df[[1]]) %>% 
    as.data.frame() %>% 
    filter(fit.class == Var2) %>% 
    summarize(count = sum(Freq)) %>% 
    as.numeric()

misclass_npct <- paste0(misclass, ' (', round(misclass / (good_class + misclass) * 100, 0), '%)')
```

```{r inlineMisc}
pctne <- calculate_percent_contribution(ds)

extractBeta <- function(data) {
    data %>%
      mutate(estCI = paste0('(beta: ', trim(format(round(estimate, 1), nsmall = 1)),
                            ' CI: ',
                            trim(format(round(conf.low, 1), nsmall = 1)),
                            ', ',
                            trim(format(round(conf.high, 1), nsmall = 1)),
                            ')'),
             #indep.estCI = paste(indep, estCI),
             #dep = paste(dep %>% gsub('log\\((.*)\\)', '\\1', .), estCI),
             dep = paste(dep %>% gsub('log\\((.*)\\)', '\\1', .))
             ) %>%
      filter(p.value <= 0.05) %>%
      arrange(dep, desc(estimate)) %>%
      select(dep, indep, estCI)
}
```

@@

`r cite_f('nefaDist')` shows the distribution of the NEFA composition. Four
individual NEFA made up the majority (`r sum(pct_nefa$pct)`%) of the total NEFA
fraction. The largest contributor was `r pctne$c[1]`, followed by `r
pctne$c[2]`, `r pctne$c[3]`, and `r pctne$c[4]`.

@@

There was poor discriminatory ability in identifying patterns between tertiles
of ISSI-2, with only `r misclass_npct` of participants in the baseline
visit who were classified correctly. In general, participants in the 3rd tertile
(a high ISSI-2) had less of all NEFA, though the mean differences between
tertiles were minor (`r cite_f('lda')`). The separation of tertiles of
log(ISSI-2) and linear discriminants is shown in `r cite_sf('lda')`.

These results confirm the findings from the longitudinal GEE modeling of
individual NEFA variables.

Results between visits were not substantially different.

@@

In a Canadian population of adults who are at-risk for diabetes, we found that
higher total NEFA independently predicted a lower beta-cell function over 6
years. In particular, the specific composition of the NEFA fraction had no
association with any of the metabolic outcomes within this cohort. These
findings suggest that the size of the total fraction, rather than the
composition, influences the pathogenesis of diabetes.

@@

Comment on LDA analysis... ...LDA backs up some of the GEE model results,
showing weak discriminatory ability of the NEFA pattern on identifying beta-cell
function... ...While the overall discriminatory ability of the NEFA pattern was
poor, there was a general pattern that most NEFA were lower in individuals with
higher beta-cell function. However, the differences between groups were minor
and confirms the findings from the GEE modeling.

@@

```{r figDist, fig.cap=fig_dist}
plot_nefa_distribution(ds)
```

```{r figGEE, dependson='geeData', fig.cap=fig_gee}
plot_gee_results(gee_results)
```

```{r figLDA, fig.cap=fig_lda}
visualize(lda_results, 'means', label.rename.fun = renaming_fa) %>% 
    vision_simple() +
    labs(y = 'Non-esterified fatty acids',
         x = 'Standardized mean of the fatty acid (SD of the nmol/mL)')
```

@@

```{r supFigGeeUnadj, dependson='geeData'}
plot_gee_results(gee_results_unadj)
```

```{r supFigLDA}
visualize(lda_results, orig.data = lda_df, group.name = 'BCF') %>% 
    vision_simple()
```
